\renewcommand{\baselinestretch}{1.5} %設定行距
\pagenumbering{roman} %設定頁數為羅馬數字
\clearpage  %設定頁數開始編譯
\sectionef
\addcontentsline{toc}{chapter}{ACKNOWLEDGMENTS} %將摘要加入目錄
\begin{center}
\LARGE\textbf{ACKNOWLEDGMENTS}\\
\LARGE\textbf{致謝}\\
\end{center}
\fontsize{14pt}{2.5pt}\sectionef
  {  I would like to thank Dr. Giulia Bruno for her expert advice and invitation to develop this project, as well as Emiliano Traini, for his extraordinary support in this thesis process.}。\\[1pt]

\fontsize{14pt}{5pt}\sectionef
  {  我要感謝朱莉婭·布魯諾博士的專家建議和邀請來開發這個
專案以及埃米利亞諾·特拉尼，感謝他在本論文過程中的非凡支持。}\\[15pt]

\fontsize{14pt}{2.5pt}\sectionef
  {  My most sincere gratitude to my parents, Julio and Michelle, who gave me everything, 
from my life to their extensive and unconditional support and encouragement; also, to my 
brothers and my fiancée Ana, who inspired me through all these years.}\\[1pt]

\fontsize{14pt}{5pt}\sectionef
  {  我最誠摯的感謝我的父母Julio和Michelle，他們給了我一切，從我的生活到他們廣泛、無條件的支持和鼓勵； 還有，對我的
兄弟們和我的未婚妻安娜這些年來一直激勵著我。}\\[15pt]

\fontsize{14pt}{2.5pt}\sectionef
{  My deepest thanks and appreciation to Icaro, Matt, and Maz, for their endless help and 
support throughout not just this project, but for all the other moments in which they pushed 
me to be better. Also, for those who have touched my life, being my greatest gifts, you all 
know who you are, and I am truly grateful for sharing special moments of my lif}\\[1pt]

\fontsize{14pt}{5pt}\sectionef
  {我對 Icaro、Matt 和 Maz 表示最深切的感謝和讚賞，感謝他們的無盡幫助，
不僅支持這個項目，還支持他們推動的所有時刻
我要變得更好。 另外，對於那些感動我生命的人，你們是我最好的禮物
知道你是誰，我真的很感激分享我生命中的特殊時刻}\\[15pt]
